---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753Jarr0004)
```

# Introduction

This is my package for documentation of the various functions used throughtout the labs.

# Function scatterhist

This creates a sophisticated scatterplot.

```{r}
x = c(1, 2, 3);
y = c(4, 5, 6);
MATH4753Jarr0004::scatterhist(x, y, "x lab", "y lab");
```

# Function mybin

This creates a sophisticated barplot using binomial

```{r}
MATH4753Jarr0004::mybin(1000, 18, 0.3);
```

# Function myncurve

Creates normal graph with the given area calculater

```{r}
MATH4753Jarr0004::myncurve(4, 2, 5);
```

# Function mysample

Creates a sohpisticated barplot of a sample

```{r}
MATH4753Jarr0004::mysample(1000, 4);
```
